Discovery of s-process enhanced stars in the LAMOST survey

### 2018-10-01 article/ms.tex
changes

The abundance of elements created through the slow neutron-capture process (s-process) is a measure of the nucleosynthetic reactions that occur primarily in Asymptotic Giant Branch (AGB) stars. Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon, and heavy elements (Z > 30) are commonly referred to as 'barium stars' \citep{Bidelman1951}. The naming convention associated with 'barium stars' is historical, for the purposes of this paper it is necessary to classify definitions used for subsequent discussions. Stars with Ba and Sr enrichment will be refereed to as s-process candidates, and singular enhancement samples will be named according to their respective element. Metallicity-dependent classifications also exist in the literature. Metal-poor stars ([Fe/H] $\approx$ [0,-1.2]) enriched by s-process elements are classically refereed to as CH stars, we will simply define them as metal poor s-process candidates. An abundance criteria may also be used to define s-process enrichment, this is typically taken as threshold of $\rm[Ba/Fe]\geq +0.3$ \citep{malaney1988}. For the purposes of this paper, s-process enrichment will be determined solely on the presence significant flux residuals as described in Section \ref{sec:cand}.
S-process candidates can be classified as either extrinsic or intrinsic objects. Extrinsic s-process stars are stellar phenomena exhibiting an enhancement as the result of some polluting process. Stars intrinsically enhanced in s-process elements are known as AGB S stars. These stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase. During this stage of nucleosynthesis, the s-process produces an over-abundance of both carbon and heavy elements. The thermal pulsing cycle transports these elements to surface of TP-AGB stars. According to the mass-transfer hypothesis, extrinsic s-process stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}. Both dynamical systems require a binary configuration with a previous TP-AGB companion star (AGB S star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}. In fact, \citet{mcclure1983} determined 85\% of all s-process candidates are in binary systems. They further claimed that stars which appeared to be singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small ranges \citep{pourbaix2004}. For these reasons, the properties and occurrence rate of s-process candidates are informative of the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.

@@

Occurring in the interior of AGB stars, the s-process synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,bisterzo2014,karakas2014}. During the subsequent TP-AGB phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the mass of the H-exhausted core. These energy bursts drive a convective zone that sweeps almost the entire region lying between the core and the He-shell, mixing the products of nucleosynthesis within these regions. While simultaneously forcing the star to expand and pushing the H-shell out to cooler regions \citep{karakas2002}. The convective envelope will then move inwards towards regions previously mixed by the thermal pulse driven convective zones. This phase of expansion and resulting inward movement is defined as the third dredge up (TDU), and is theorised to occur after each thermal pulse. During the TP-AGB phase, the TDU is responsible for the surface enrichment in $^{12}$C and heavy elements produced by the s-process \citep[e.g.,][]{busso2001}. Post dredge up the star contracts, reigniting the H-shell and producing the majority of the surface luminosity for the next interpulse period. The interpulse, thermal pulse, and dredge up cycle may occur numerous times and the frequency depends on the initial mass, composition, and mass-loss rate of the star.

S-process candidates can form within a metallicity-dependent initial mass range of approximately $0.8 - 8\,M_{\odot}$ \citep{karakas2016cp}. The minimum mass is defined by the onset of core helium burning, and the maximum by core carbon burning. The age of these stars varies considerably, with some reaching ages $\approx$ 12\,Gyr in metal-poor globular clusters. Less massive metal-rich stars may reach ages of $\approx$ 100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}. The majority of s-process candidates are observed to be members of the disk \citep{jorissen1993,gomez1997,mennessier1997}. In \citet{pereira2011}, it is shown that metal-rich s-process candidates share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population. \cite{jorissen1993} relates galactic position to the extrinsic or intrinsic nature of the s-process candidate. They determine the scale height for their intrinsic candidates and state they are concentrated towards the galactic plane whilst their extrinsic s-process candidates are uniformly distributed.

In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015} and identify 895 s-process candidates. In Section \ref{sec:methods} we describe the observations and candidate selection. Section \ref{sec:observations} details the analysis of high-resolution follow-up observations obtained for a few candidates. In Section \ref{sec:dis} we discuss the properties of our s-process candidates in context of existing literature. We provide concluding remarks in Section \ref{sec:con}.

\section{Methods} \label{sec:methods}
\subsection{LAMOST analysis}
\subsubsection{Data-driven analysis}
The LAMOST (Large sky Area Multi-Object Fibre Spectrographic) survey released low-resolution ($\mathcal{R} \approx 1800$) optical spectra (3700\,\AA\ to 9000\,\AA) for 2,207,189 stars in their second data release \citep{luo2015}. Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived by \citep{ho2017} using a \emph{The Cannon} \citet{ness2016}, with labels for 9,952 giant stars in common between LAMOST and the APOGEE survey. Our sample is limited entirely to giants implying that we would not identify dwarf s-process enhanced stars. Cross-validation tests shows that the typical uncertainties are approximately 70\,K in effective temperature $\rm T_{\rm eff}$, 0.1\,dex in surface gravity $\log{g}$, 0.1\,dex in metallicity [M/H], and 0.04\,dex in the $\alpha$-element abundance relative to overall metallicity [$\alpha$/M]. These uncertainties are comparable to the those present in APOGEE \citep{alam2015}.

\subsubsection{Candidate selection} \label{sec:cand}
The s-process candidates in this work were identified by filtering for significant flux residuals. We fit a Gaussian distribution with amplitude A to the flux residuals at each s-process element absorption line. These included; 4554\,\AA\ (\ion{Ba}{II}) and 4077\,\AA\ (\ion{Sr}{II}) wavelengths for s-process candidates, 4554\,\AA\ (\ion{Ba}{II}) and 4934\,\AA\ (\ion{Ba}{II}) wavelengths for barium enriched candidates, and wavelengths at 4077\,\AA\ (\ion{Sr}{II}) and 4215\,\AA\ (\ion{Sr}{II}) for strontium enriched candidates. The amplitude of each Gaussian fit at each wavelength is analogous to the depth of each absorption line. The discrepancy is then measured as the difference between the normalised LAMOST flux and the data driven model. A negative residual indicates enrichment, this is shown for a randomly chosen s-process candidate in Figure \ref{fig:figure1}.
We used five filters for each spectrum and subsequent set of absorption lines in order to identify s-process enrichment, these included:

@@

\begin{enumerate} 
\item Profile amplitude for both enhancement lines must be $A < -0.05$, indicating a stronger absorption line than expected by the model.
\item Both amplitudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
\item The wavelength at each absorption line must be within 2\,\AA\ ($\lambda$ < 2) of the rest frame laboratory model.
\item The reduced $\chi^2$ from \emph{The Cannon} must be $\chi_r^2 < 3$.
\item The LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
\end{enumerate}
We use visual inspection with all candidates to exclude any results containing false positives: candidates with data reduction issues; apparent absorption finer then the spectral resolution; or overly noisy normalised LAMOST spectra. This approach discovers 895 s-process rich candidates which are provided in Table 1. This sample consists of; 187 s-process candidates, 49 barium enriched stars, and 659 stars with strontium enrichment. It is the largest collection of s-process enhanced stars ever discovered.

@@

\subsubsection{Enhancements due to sodium, technetium, and carbon} \label{sec:other enhancements}
Enhancements in sodium, technetium, and carbon are useful indicators when determining whether a sample is populated by intrinsically enhanced AGB S stars, or polluted extrinsic barium stars. We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify negative flux residuals for enhancement in sodium, technetium, or carbon. For sodium enrichment, we required significant absorption in the doublet lines at 5889\,\AA\ and 5895\,\AA\. Only 5/187 s-process candidates met this criteria. For technetium enhancement, we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. These absorption lines are extremely weak, and would require a substantial amount of technetium enhancement before it would be visible in a high S/N LAMOST spectrum. We found that 51 s-process candidates exhibited some level of significant enhancement at the single absorption line 4238\,\AA. Single line enrichment discovered by our data driven approach are very likely attributed to data reduction/calibration artefacts present. These artefacts exist within in our data as a result of fitting a model to the LAMOST spectral data. As such, the 51 stars enhanced in a single Tc line can be ruled out as false positives. For carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA, of which 178/187 s-process candidates exhibited significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).

@@

\subsubsection{Abundances estimated from LAMOST spectra}
We estimated [Ba/Fe] and [Sr/Fe] abundance ratios for all s-process enhanced candidates by synthesising spectra. We assumed that absorption due to metals is captured by \emph{The Cannon} model, and deviations in flux at the 4554\,\AA\ \ion{Ba}{II} line and the 4077\,\AA\ \ion{Sr}{II} transition are solely due to enhancements in Ba and Sr, respectively. We used an extensive grid of model
atmospheres developed by the MARCS program \citep{marcs}, determined stellar parameters using the SME code\citep{sme},?

In analyses of stellar spectra and colours, and for the analysis of integrated light from galaxies, a homogeneous grid of model
atmospheres of late-type stars and corresponding flux spectra is needed
We construct an extensive grid of spherically-symmetric models (supplemented with plane-parallel ones for the highest surface
gravities), built on up-to-date atomic and molecular data, and make it available for public use.

\citep{marcs,sme,vald,ispec}. We adopted the stellar parameters ($T_{\rm eff}$, $\log{g}$, [Fe/H]) from \citet{ho2017}, and assume a microturbulence of $v_{mic} = 2\,{\rm km\,s}^{-1}$. Uncertainties in [Ba/Fe] and [Sr/Fe] from LAMOST are taken as the fitting error due to noise, added in quadrature with an adopted $0.2\,{\rm dex}$ systematic error floor.

Our analysis shows 186/187 of our s-process candidates exhibit enhancement at the BaII resonance line 4554 with a $\rm[Ba/Fe] \geq +0.3$, and a average abundance error of 0.1. Previous studies \citet{malaney1988} have defined s-process candidates through an abundance criteria of $\rm[Ba/Fe]\geq +0.3$. Using this measure, only one star ($\rm J092155.95+265253.4$) from our sample exhibits a lower [Ba/Fe] of 0.12. This however does not rule out s-process enhancement for this candidate. As previously discussed, a negative residual at the \ion{Ba}{II} resonance line 4554\,\AA\ indicates s-process enhancement and as discussed in section \ref{sec:other enhancements}, carbon enrichment is observed frequently with s-process enhancement. $\rm J092155.95+265253.4$ shows both a negative residual at 4554\,\AA\ and carbon enrichment, we therefore conclude that this single deviant case can be classified as a s-process candidate. This additionally applies to candidates that fall under $\rm[Ba/Fe]\geq +0.3$ due to the average abundance error.

\subsection{Dynamics}
We integrated the galactic orbits using recent astrometry from Gaia \citep{gaia2016,gaia2018b, cropper2018, katz2018, lindegren2018, sartoretti2018} for 871/895 s-process enhanced stars with parallax > 0 and parallax/parallax error > 5 selection filters. We integrated each star backwards for $0.5\,\textrm{Gyr}$ using the \texttt{gala} Python package \citep{price2017} in a Milky Way-like potential \citep{mwpotential2014} that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and a \citet{nfw1997} halo. We computed spatial velocities relative to the local standard of rest, where $U_{LSR}$ is positive towards the Galactic centre, $V_{LSR}$ is positive in the direction of Galactic rotation ($l=90^{\circ}, b=0^{\circ}$), and $W_{LSR}$ is positive towards the north galactic pole ($b=90^{\circ}$). Our analysis revealed 97\% disk star membership and 3\% with velocity consistent to the halo which is shown using a Toomre diagram in Figure \ref{fig:figure4}.

@@

\subsection{Observations and data reduction}
On 07 January 2018 we acquired a high-resolution spectrum of two s-process candidates (J09162834+0259348 and J08351472-0548480) using the MIKE (Magellan Inamori Kyocera Echelle) \citep{bernstein2003} spectrograph on the Magellan Clay telescope \citep{schectman2003} at Las Campanas Observatory, Chile. These two candidates were observed as part of another program not a detailed follow-up campaign. They were selected based on observability constraints and ranked by their apparent visual magnitude, with both candidates having $V \approx 12$. We observed both stars in good seeing using the 0.7 arcsecond slit and 2x2 spatial on-chip binning, providing a spectral resolution of $\mathcal{R} \approx 28,000$. Exposure times of 100 seconds were sufficient to achieve a S/N ratio exceeding 30 per pixel at 4500\,\AA. We acquired calibration (biases, milky, quartz, and Th-Ar arc lamp) frames in the afternoon. We reduced the data using the \texttt{CarPy} package \citep{kelson2000}. We used spline functions to continuum-normalise all echelle orders, and resampled the normalised spectra onto a uniform-spaced wavelength map. We used a rest-frame normalised template of a FGK-type star to place the observed spectra at rest.

@@

\subsection{Extrinsic or intrinsic}
S-process enrichment can be explained by intrinsic or extrinsic phenomena. Intrinsically enhanced s-process candidates must be massive enough to reach the TP-AGB phase, and extrinsic s-process candidates must be in a binary with a previously polluting TP-AGB star companion (AGB S star). Previous literature \citep{van2017} \hspace{0.3mm} states only 33\% of their sample are post-main-sequence s-process candidates (extrinsic). In comparison, Figure \ref{fig:figure2} shows that the majority of our sample are within temperature and log g ranges consistent with RGB populations. This highlights that our sample does not contain stars evolved enough to reach the TP-AGB phase and therefore, must be extrinsic s-process candidates. This is in agreement with our sample selection bias given we were predominantly restricted to RGB stars. However stars with temperatures below 3800K in Figure \ref{fig:figure2} are possible AGB candidates, and their intrinsic or extrinsic nature is not certain.

@@

%however, these [Na/Fe] ratios do not exhibit variations in metallicity
We find that less than $3$\,\% of our s-process candidates show enhanced sodium all of which have values of $\log{g} \approx 3$. It is possible our 5/187 enhanced sodium candidates are false-positives resulting from interstellar dust absorption. Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2/5 of these candidates have E(B-V)$\approx$ 0.35 confirming that the flux residuals around the Na doublet are due to interstellar absorption. However 3/5 candidates exhibit low ($\approx$0.045) E(B-V) values indicating the enhancement is more likely due to stellar absorption. These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 3 s-process candidates. It also highlights sodium enhancement is by no means ubiquitous in s-process candidates. Yet, low resolution spectra can imitate Na line saturation and limits flux enhancement even if an abundance enhancement is present.
%Previous studies \citep[e.g.,][]{decastro2016} suggest lower $\log{g}$ values systematically contribute to higher [Na/Fe] abundance ratios.

The data that led \citet{decastro2016} to conclude that s-process candidates have higher [Na/Fe] ratios is subject to systematic differences (biases) between Milky Way studies of normal FGK-type stars, and those focussed on s-process candidates. This has the potential to contain unresolved differences in the reported [Na/Fe] abundance ratio. These systematic effects would also contribute to the observed correlation between [Na/Fe] and $\log{g}$, since intrinsic s-process candidates (by definition) have low $\log{g}$ values. We do not observe this correlation between [Na/Fe] and $\log{g}$ in our sample. We find that s-process candidates do not have higher [Na/Fe] abundance ratios on average.

@@

\subsection{Carbon bands}
During the AGB phase of a star, carbon abundance is a product of helium fusion via the triple-alpha process. Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star. Our analysis identifies carbon enhanced candidates by searching for flux residuals in the CH and G band regions near 4300\,\AA. We found 178/187 of our s-process candidates to have carbon enrichment (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$). These 178 stars have metallicities ranging of 0 to -1.2 and are classically referred to as CH stars \citep[e.g.][]{luck1991, mcclure1997}. We simply define them as metal poor s-process candidates.

>>>>

The abundance of elements created through the slow neutron-capture process (s-process) is primarily a measure of the nucleosynthetic reactions that occur primarily in Asymptotic Giant Branch (AGB) stars. Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon, and heavy elements (Z > 30) are commonly referred to as 'barium stars' \citep{Bidelman1951}. The naming convention associated with 'barium stars' is historical, and for the purposes of this paper it is necessary to classify definitions used for subsequent discussions. Throughout this work we will refer to `s-process candidates' as stars with both Ba and Sr enrichment, and stars with just strong Sr enrichment or strong Ba enrichment will be referred to as Sr-rich or Ba-rich candidates. Metallicity-dependent classifications also exist in the literature. Metal-poor stars ([Fe/H] $\approx$ [0,-1.2]) enriched by s-process elements are classically refereed to as CH stars, whereas here we will simply define them as metal-poor s-process candidates. 
%An abundance criteria is also commonly used to define s-process enrichment, typically taken as a threshold of $\rm[Ba/Fe]\geq +0.3$ \citep{malaney1988}. For the purposes of this paper, s-process enrichment will be determined solely on the presence significant flux residuals as described in Section \ref{sec:cand}.

Extrinsic or intrinsic mechanisms can be invoked to explain s-process enrichment in a given star.
%S-process candidates can be classified as either extrinsic or intrinsic objects. 
This refers to the source of the enrichment, either a mechanism intrinsic to the star, or an extrinsic process (e.g., pollution) that resulted in an over-abundance of s-process elements.
%Extrinsic s-process stars are stellar phenomena exhibiting an enhancement as the result of some polluting process.
Stars intrinsically enhanced in s-process elements are known as AGB S stars. These stars are in the thermally pulsing asymptotic giant branch (TP-AGB) phase. During this stage of nucleosynthesis, the slow neutron capture process produces an over-abundance of both carbon and heavy elements, and the thermal pulsing cycle transports these elements to surface of the star. According to the mass-transfer hypothesis, extrinsic s-process stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}. Both dynamical systems require a binary configuration with a previous TP-AGB companion star (AGB S star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}. In fact, \citet{mcclure1983} determined 85\% of all s-process candidates are in binary systems. They further claimed that stars which appeared to be singular stars are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small range \todo{of inclination angles?} \citep{pourbaix2004}. For these reasons, the properties and occurrence rate of s-process candidates are informative of the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.

@@

The s-process synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,bisterzo2014,karakas2014}. During the thermal pulsing phase of AGB stars, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the mass of the H-exhausted core. These energy bursts drive a convective zone that sweeps almost the entire region lying between the core and the He-shell, mixing the products of nucleosynthesis within these regions. \todo{While simultaneously forcing the star to expand and pushing the H-shell out to cooler regions \citep{karakas2002}.} The convective envelope will then move inwards towards regions previously mixed by the thermal pulse driven convective zones. This phase of expansion and resulting inward movement is defined as the third dredge up (TDU), and is theorised to occur after each thermal pulse. During the TP-AGB phase, the TDU is responsible for the surface enrichment in $^{12}$C and heavy elements produced by the s-process \citep[e.g.,][]{busso2001}. Post dredge up the star contracts, reigniting the H-shell and producing the majority of the surface luminosity for the next interpulse period. The interpulse, thermal pulse, and dredge up cycle may occur numerous times and the frequency depends on the initial mass, composition, and mass-loss rate of the star.

S-process candidates can form within a metallicity-dependent initial mass range of approximately $0.8 - 8\,M_{\odot}$ \citep{karakas2016cp}. The minimum mass is defined by the onset of core helium burning, and the maximum is set by core carbon burning. The age of these stars varies considerably, with some reaching ages $\approx$ 12\,Gyr in metal-poor globular clusters. Less massive metal-rich stars may reach ages of $\approx$ 100Myr, including  stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}. The majority of s-process candidates are observed to be members of the disk \citep{jorissen1993,gomez1997,mennessier1997}. In \citet{pereira2011}, it was shown that metal-rich s-process candidates share similar kinematics to other metal-rich and super metal-rich stars already known, suggesting that they do not belong exclusively to the bulge. \cite{jorissen1993} relates galactic position to the extrinsic or intrinsic nature of their s-process candidates. They determine the scale height for their intrinsic candidates and demonstrate they are concentrated towards the galactic plane, whilst their extrinsic s-process candidates are uniformly distributed in absolute galactic latitude. \todo{OK,.. so maybe a comment on why that is scientifically important? what insight does that give?}

In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015}, and identify 895 s-process candidates using a data-driven approach. In Section \ref{sec:methods} we describe the observations and candidate selection. Section \ref{sec:observations} details the analysis of high-resolution follow-up observations obtained for a few candidates. In Section \ref{sec:dis} we discuss the properties of our s-process candidates in context of existing literature. We provide concluding remarks in Section \ref{sec:con}.

\section{Methods} \label{sec:methods}
\subsection{LAMOST analysis}
\subsubsection{Data-driven analysis}
The LAMOST (Large sky Area Multi-Object Fibre Spectrographic) survey released low-resolution ($\mathcal{R} \approx 1800$) optical spectra (3700\,\AA\ to 9000\,\AA) for 2,207,189 stars in their second data release \citep{luo2015}. Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived by \citep{ho2017} using a \emph{The Cannon} \citet{ness2016}, with labels for 9,952 giant stars in common between LAMOST and the APOGEE survey. Our sample is limited entirely to giant stars, implying that we would not identify dwarf s-process enhanced stars. Cross-validation tests shows that the typical uncertainties are approximately 70\,K in effective temperature $\rm T_{\rm eff}$, 0.1\,dex in surface gravity $\log{g}$, 0.1\,dex in metallicity [M/H], and 0.04\,dex in the $\alpha$-element abundance relative to overall metallicity [$\alpha$/M]. These uncertainties are comparable to the those present in APOGEE \citep{alam2015}.

\subsubsection{Candidate selection} \label{sec:cand}
The s-process candidates in this work were identified by filtering for significant flux residuals. We fit a Gaussian function with amplitude A to the flux residuals at each s-process element absorption line. This includes; 4554\,\AA\ (\ion{Ba}{II}) and 4077\,\AA\ (\ion{Sr}{II}) wavelengths for s-process candidates, 4554\,\AA\ (\ion{Ba}{II}) and 4934\,\AA\ (\ion{Ba}{II}) wavelengths for barium enriched candidates, and wavelengths at 4077\,\AA\ (\ion{Sr}{II}) and 4215\,\AA\ (\ion{Sr}{II}) for strontium enriched candidates. The amplitude of each Gaussian fit at each wavelength is analogous to the depth of each absorption line. The discrepancy is then measured as the difference between the normalised LAMOST flux and the data driven model. A negative residual indicates enrichment, which is shown for a randomly chosen s-process candidate in Figure \ref{fig:figure1}.
We used five filters for each spectrum and subsequent set of absorption lines in order to identify s-process enrichment, these included:

@@

\begin{enumerate} 
\item Profile amplitude for both enhancement lines must be $A < -0.05$, indicating a stronger absorption line than expected by the model.
\item Both amplitudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
\item The wavelength at each absorption line must be within 2\,\AA\ ($\lambda$ < 2) of the rest frame laboratory model.
\item The reduced $\chi^2$ from \emph{The Cannon} must be $\chi_r^2 < 3$.
\item The LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
\end{enumerate}
In addition to requiring matches at two wavelengths (e.g., both 4934\,\AA\ and 4554\,\AA\ for barium enriched candidates), we visually inspected all candidates to exclude any  obvious false positives: candidates with data reduction issues; apparent absorption finer then the spectral resolution; or overly noisy spectra. This approach yielded 895 candidates, the details of which are tabulated in Table 1, and includes 187 s-process candidates, 49 barium enriched stars, and 659 stars with just strontium enrichment. This constitutes the largest collection of s-process enhanced stars ever discovered. \todo{what is the next biggest sample?}

@@

\subsubsection{Enhancements due to sodium, technetium, and carbon} \label{sec:other enhancements}
Enhancements in sodium, technetium, and carbon are useful indicators when determining whether a sample is populated by intrinsically enhanced AGB S stars, or polluted extrinsic barium stars. We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify negative flux residuals for enhancement in sodium, technetium, or carbon. For sodium enrichment, we required significant absorption in the doublet lines at 5889\,\AA\ and 5895\,\AA\. Only 5/187 s-process candidates met this criteria. For technetium enhancement, we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. These absorption lines are extremely weak, and would require a substantial amount of technetium enhancement before it would be visible in a high S/N LAMOST spectrum. We found that 51 s-process candidates exhibited some level of significant enhancement at the single absorption line 4238\,\AA. However, single line enrichment discovered by our data driven approach are very likely attributed to data reduction/calibration artefacts present, and none of these candidates exhibited Tc enrichment at any other absorption line. As such, we discard these 51 stars with enhancement at a single Tc absorption line as false positives. For carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA, of which 178/187 s-process candidates exhibited significant carbon enhancement.% (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).

@@

\subsubsection{Abundances estimated from LAMOST spectra}
We estimated [Ba/Fe] and [Sr/Fe] abundance ratios for all s-process enhanced candidates by spectrum synthesis. We assumed that absorption due to most metal lines is captured by \emph{The Cannon} model, and deviations in flux at the 4554\,\AA\ \ion{Ba}{II} line and the 4077\,\AA\ \ion{Sr}{II} transition are solely due to enhancements in Ba and Sr, respectively. We used the grid of MARCS model atmospheres \citep{marcs}, atomic transitions from VALD \citep{vald}, and the SME code \citep{sme,ispec} to synthesise spectra of each star, and varied the Ba and Sr abundances until they matched the flux deviations away from our data-driven model. We adopted the stellar parameters ($T_{\rm eff}$, $\log{g}$, [Fe/H]) from \citet{ho2017}, and assume a microturbulence of $v_{mic} = 2\,{\rm km\,s}^{-1}$. Uncertainties in [Ba/Fe] and [Sr/Fe] from LAMOST are taken as the fitting error due to noise, added in quadrature with an adopted $0.2\,{\rm dex}$ systematic error floor.

Previous studies have used a $\textrm{[Ba/Fe]} > +0.3$ threshold to define a star being a s-process candidate \citep{malaney1988}. Our abundance analysis shows 186/187 of our s-process candidates -- identified from flux residuals alone -- meet this criteria based on spectrum synthesis of the 4554\,\AA\ transition. Using this measure, only one star ($\rm J092155.95+265253.4$) from our sample exhibits a lower [Ba/Fe] of 0.12. This however does not rule out s-process enhancement for this candidate. As previously discussed, a negative residual at the \ion{Ba}{II} resonance line 4554\,\AA\ indicates s-process enhancement and as discussed in section \ref{sec:other enhancements}, carbon enrichment is observed frequently with s-process enhancement. $\rm J092155.95+265253.4$ shows both a negative residual at 4554\,\AA\ and carbon enrichment, we therefore conclude that this single deviant case can be classified as a s-process candidate. 
%This additionally applies to candidates that fall under $\rm[Ba/Fe]\geq +0.3$ due to the average abundance error.

\subsection{Dynamics}
We integrated the galactic orbits using recent astrometry from the second Gaia data release \citep{gaia2016,gaia2018b, cropper2018, katz2018, lindegren2018, sartoretti2018} for 871/895 s-process enhanced stars with positive parallaxes ($\varpi > 0$) and parallax S/N of five or above ($\varpi/\sigma_\varpi > 5$). We integrated each star backwards for $0.5\,\textrm{Gyr}$ using the \texttt{gala} Python package \citep{price2017} in a Milky Way-like potential \citep{mwpotential2014} that consists of three components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and a \citet{nfw1997} halo. We computed spatial velocities relative to the local standard of rest, where $U_{LSR}$ is positive towards the Galactic centre, $V_{LSR}$ is positive in the direction of Galactic rotation ($l=90^{\circ}, b=0^{\circ}$), and $W_{LSR}$ is positive towards the north galactic pole ($b=90^{\circ}$). Our analysis revealed 97\% disk star membership and 3\% with velocity consistent to the halo which is shown using a Toomre diagram in Figure \ref{fig:figure4}.

@@

\subsection{Observations and data reduction}
On 07 January 2018 we acquired a high-resolution spectrum of two s-process candidates (J09162834+0259348 and J08351472-0548480) using the MIKE (Magellan Inamori Kyocera Echelle) \citep{bernstein2003} spectrograph on the Magellan Clay telescope \citep{schectman2003} at Las Campanas Observatory, Chile. These two candidates were observed as part of another program, and do not represent a comprehensive follow-up observational campaign. These targets were selected based on observability constraints and ranked by their apparent visual magnitude, with both candidates having $V \approx 12$. We observed both stars in good seeing using the 0.7 arcsecond slit and 2x2 spatial on-chip binning, providing a spectral resolution of $\mathcal{R} \approx 28,000$. Exposure times of 100 seconds were sufficient to achieve a S/N ratio exceeding 30 per pixel at 4500\,\AA. We acquired calibration (biases, milky, quartz, and Th-Ar arc lamp) frames in the afternoon. We reduced the data using the \texttt{CarPy} package \citep{kelson2000}. We used spline functions to continuum-normalise all echelle orders, and resampled the normalised spectra onto a uniform-spaced wavelength map. We used a rest-frame normalised template of a FGK-type star to place the observed spectra at rest.

@@

\subsection{Extrinsic or intrinsic}
S-process enrichment can be explained by intrinsic or extrinsic mechanisms. Intrinsically enhanced s-process candidates must be massive enough to reach the TP-AGB phase, and extrinsic s-process candidates must be in a binary with a previously polluting TP-AGB star companion (AGB S star). \citet{van2017} found that only 33\% of their sample are post-main-sequence s-process candidates (extrinsic). In comparison, Figure \ref{fig:figure2} shows that the majority of our sample are within temperature and surface gravity ranges consistent with the first ascent giant branch. This highlights that our sample does not appear to contain many stars evolved enough to reach the TP-AGB phase and therefore, must be extrinsic s-process candidates. However stars with $\log{g} \lesssim 2$ in Figure \ref{fig:figure2} are possible AGB star candidates, and their intrinsic or extrinsic nature is not certain.

%This is in agreement with our sample selection bias given we were predominantly restricted to RGB stars. However stars with temperatures below 3800K in Figure \ref{fig:figure2} are possible AGB candidates, and their intrinsic or extrinsic nature is not certain.

@@

%however, these [Na/Fe] ratios do not exhibit variations in metallicity
We find that only 5/187 s-process candidates ($<3$\,\%) show enhanced sodium, and all 5 have  $\log{g} \approx 3$. Moreover, it is likely that some of these stars appear to have high sodium due to interstellar dust lines of Na being misinterpreted as stellar absorption. 
Using the IRSA's all-sky dust map \citep{schlafly2011}, we find that 2/5 of these candidates have E(B-V)$\approx$ 0.35, suggestive that the flux residuals around the Na doublet are due to interstellar absorption. However 3/5 candidates exhibit low ($\approx$0.045) E(B-V) values, indicating the enhancement is more likely due to stellar absorption. These results suggest that sodium-rich material from a companion TP-AGB star has polluted these 3 s-process candidates. It also highlights sodium enhancement is by no means ubiquitous in s-process candidates. %Yet, low resolution spectra can imitate Na line saturation and limits flux enhancement even if an abundance enhancement is present.
%Previous studies \citep[e.g.,][]{decastro2016} suggest lower $\log{g}$ values systematically contribute to higher [Na/Fe] abundance ratios.

The data that led \citet{decastro2016} to conclude that s-process candidates have higher [Na/Fe] ratios is subject to systematic differences (biases) between Milky Way studies of normal FGK-type stars, and those focused on s-process candidates. Specifically, the  comparisons made by \citet{decastro2016} included  [Na/Fe] abundance ratios that were derived from different stellar populations, using different abundance analysis techniques.
This has the potential to amplify systematic differences in the reported [Na/Fe] abundance ratio. These systematic effects would also contribute to the observed correlation between [Na/Fe] and $\log{g}$, since intrinsic s-process candidates (by definition) have low $\log{g}$ values. We do not observe this correlation between [Na/Fe] and $\log{g}$ in our sample. We find that s-process candidates do not have higher [Na/Fe] abundance ratios on average.

@@

\subsection{Carbon bands}
During the AGB phase of a star, carbon is produced through helium fusion during the triple-alpha process. Giants and supergiants become enhanced in carbon through TDU process discussed in Section \ref{sec:intro}, and extrinsic carbon enhancement occurs via mass transfer from a binary AGB star. Our analysis identifies carbon enhanced candidates by searching for flux residuals in the CH and G band regions near 4300\,\AA. We found 178/187 of our s-process candidates to have carbon enrichment. These 178 stars have metallicities ranging from [Fe/H] = $-1.2$ to [Fe/H] $= 0$ and would classically be described in the literature as CH stars \citep[e.g.][]{luck1991, mcclure1997}. We simply define them as metal poor s-process candidates.
